---
title: "r4ds Ex 13"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
author: MW
output: 
  pdf_document: 
    latex_engine: lualatex
documentclass: ltjsarticle
---

```{r setup, include = FALSE}
library(tidyverse)
```


# 13.1
## 1

>    
> Imagine you wanted to draw (approximately) the route each plane flies from its origin to its destination. What variables would you need? What tables would you need to combine?
> 

We need to combine `flights` and `airport` due to requiring latitude and longitude of airports of destination.

## 2

>  
> I forgot to draw the relationship between `weather` and `airports`. What is the relationship and how should it appear in the diagram?
>

`airports$faa` and `weather$origin` are relationships as foreign keys.

## 3

>
> `weather` only contains information for the origin (NYC) airports. If it contained weather records for all airports in the USA, what additional relation would it define with `flights`?
>

There are weather of destinations.

## 4

>
> We know that some days of the year are “special”, and fewer people than usual fly on them. How might you represent that data as a data frame? What would be the primary keys of that table? How would it connect to the existing tables?
>

```{r}
holiday <- tribble(
	~year, ~month, ~day, ~holiday,
	2013, 01, 01, "New Year",
	2013, 12, 25, "Christmas Day"
)
```

# 13.3
## 1

>
> Add a surrogate key to flights.
>


```{r}
flights %>% mutate(id=1:nrow(.))
```


## 2

>
> Identify the keys in the following datasets 
> > 1. Lahman::Batting, 
> > 2. babynames::babynames
> > 3. nasaweather::atmos
> > 4. fueleconomy::vehicles
> > 5. ggplot2::diamonds
> (You might need to install some packages and read some documentation.)
>

### 1.
In 1.-4. there are primary keys of each dataset.

```{r}
Lahman::Batting %>% as_tibble() %>%
	group_by(playerID, yearID, stint) %>% #grouping by primary keys
	mutate(count=n()) %>%
	filter(count>1)
```
 
Basically, 2.-4. are same as 1.

### 5
There are no primary keys.

```{r}
ggplot2::diamonds %>%
	distinct() %>%
	nrow()
ggplot2::diamonds %>%
	nrow()
```


## 3

>
> Draw a diagram illustrating the connections between the `Batting`, `Master`, and `Salaries` tables in the Lahman package. Draw another diagram that shows the relationship between `Master`, `Managers`, `AwardsManagers`.
> How would you characterise the relationship between the `Batting`, `Pitching`, and `Fielding` tables?
>

We can create diagram in R using `DiagrameR` or `datamodelr`.

```{r, eval=FALSE}
DiagrammeR::grViz("13Ex/1.dot")
DiagrammeR::grViz("13Ex/2.dot")
```

1.dot
```
digraph subgraph_label {
  rankdir = TB
  subgraph cluster0{
    yearID_S[label="yearID"]
    teamID_S[label="teamID"]
    playerID_S[label="playerID"]
    label = "Salaries"
    {rank = same; yearID; teamID; playerID;}
  }
  subgraph cluster1{
    playerID_M[label="playerID"]
    label = "Master"
  }
  subgraph cluster2{
    playerID_B[label="playerID"]
    yearID_B[label="yearID"]
    stint_B[label="stint"]
    label = "Batting"
    {rank = same; yearID; stint; playerID;}
  }
  playerID_M -> playerID_S
  playerID_M -> playerID_B
}
```

2.dot
```
digraph subgraph_label {
  rankdir = TB
  subgraph cluster0{
    yearID_MN[label="yearID"]
    teamID_MN[label="teamID"]
    playerID_MN[label="playerID"]
    inseason_MN[label="inseason"]
    label = "Managers"
    {rank = same; yearID_MN; teamID_MN; inseason_MN; playerID_MN}
  }
  subgraph cluster1{
    playerID_M[label="playerID"]
    label = "Master"
  }
  subgraph cluster2{
    playerID_A[label="playerID"]
    awardID_A[label="awardID"]
    yearID_A[label="yearID"]
    lgID_A[label="lgID"]
    label = "AwardManagers"
    {rank = same; yearID; stint; playerID;}
  }
  playerID_M -> playerID_A
  playerID_M -> playerID_MN
}
```


# 13.4
## 1

>
> Compute the average delay by destination, then join on the airports data frame so you can show the spatial distribution of delays. Here’s an easy way to draw a map of the United States: 
>


```{r}
flights %>%
	group_by(dest) %>%
	summarise(delay = mean(arr_delay, na.rm = TRUE)) %>%
	inner_join(airports, by = c(dest = "faa")) %>%
	ggplot(aes(lon, lat, colour = delay)) +
	borders("state") +
	geom_point() +
	coord_quickmap()
```


## 2

>
> Add the location of the origin and destination (i.e. the `lat` and `lon`) to `flights`. 
>

```{r}
flights %>% select(year:day, hour, origin, dest) %>%
	left_join(
		  airports,
		  by = c("origin" = "faa")
		  ) %>%
	left_join(
		  airports,
		  by = c("dest" = "faa")
	) %>%
	select(year:day, origin, dest, lat.x, lon.x, lat.y, lon.y)
```

## 3 

>
> Is there a relationship between the age of a plane and its delays?
> 

```{r}
flights %>% inner_join(planes %>% select(tailnum, plane_year = year), by = "tailnum") %>%
	mutate(age = year - plane_year) %>%
	group_by(age) %>%
	summarise(
		  dep_delay_mean = mean(dep_delay, na.rm = TRUE),
		  arr_delay_mean = mean(arr_delay, na.rm = TRUE),
		  n_arr_delay = sum(!is.na(arr_delay)),
		  n_dep_delay = sum(!is.na(arr_delay))
		  ) %>%
	ggplot(aes(x=age, y=dep_delay_mean)) +
	geom_point()
```

## 4

>
> What weather conditions make it more likely to see a delay?
>

```{r}
flights %>% 
	inner_join(weather, by = c("origin" = "origin",
				   "year" = "year",
				   "month" = "month",
				   "day" = "day",
				   "hour" = "hour"
				   )
	)
```

GLM...?


## 5

>
> What happened on June 13, 2013? Display the spatial pattern of delays, and then use Google to cross-reference with the weather.
>

There were storms.


# 13.5.1
## 1

>
> What does it mean for a flight to have a missing `tailnum`? What do the tail numbers that don’t have a matching record in planes have in common? (Hint: one variable explains ~90% of the problems.)
>

```{r}
flights %>%
	anti_join(planes, by = "tailnum") %>%
	group_by(carrier) %>%
	summarize(count=n()) %>%
	select(carrier, count)
```

## 2

>
> Filter flights to only show flights with planes that have flown at least 100 flights.
>

```{r}
flights %>%
	group_by(tailnum) %>%
	count() %>%
	filter(n >= 100)
```


## 3

>
> Combine `fueleconomy::vehicles` and `fueleconomy::common` to find only the records for the most common models.
>

```{r}
fueleconomy::vehicles %>%
	semi_join(fueleconomy::common, by = c("make", "model")) %>%
	distinct(model, make) %>%
	group_by(model) %>%
	mutate(count=n()) %>%
	filter(count > 1) %>%
	arrange(count)
```

## 4

>
> Find the 48 hours (over the course of the whole year) that have the worst delays. Cross-reference it with the weather data. Can you see any patterns?
>

```{r}
flights %>%
	mutate(hour=sched_dep_time %/% 100) %>%
	group_by(origin, year, month, day, hour) %>%
	summarise(dep_delay = mean(dep_delay, na.rm = TRUE)) %>%
	arrange(desc(dep_delay)) %>%
	slice(1:48) %>%
	inner_join(weather, by=c("origin", "year", "month", "day", "hour")) %>%
	ggplot(aes(x = precip, y = wind_speed, color = temp)) +
	geom_point()
```

## 5

>
> What does `anti_join(flights, airports, by = c("dest" = "faa"))` tell you? What does `anti_join(airports, flights, by = c("faa" = "dest"))` tell you?
>


