---
title: "r4ds Ex 7.3.4"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
author: MW
output: pdf_document
---

```{r setup, include = FALSE}
library(tidyverse)
```


# 7.3.4
## 1
>    
> Explore the distribution of each of the `x`, `y`, and `z` variables in `diamonds`. What do you learn? Think about a diamond and how you might decide which dimension is the length, width, and depth.  
>

```{r}
diamonds %>% select(x,y,z) %>% summary
```

```{r}
diamonds %>% select(x,y,z) %>% 
	gather() %>% 
	ggplot(aes(x=value, fill = key)) +
	geom_histogram(position = "fill")
```



## 2
>  
> Explore the distribution of price. Do you discover anything unusual or surprising? (Hint: Carefully think about the `binwidth` and make sure you try a wide range of values.)
>

## 3
>  
> How many diamonds are 0.99 carat? How many are 1 carat? What do you think is the cause of the difference?
>

```{r}

diamonds %>% filter(carat >= 0.99, carat <= 1) %>%
	count(carat)
```

These results inply that many diamonds are rounded up.


## 4
>  
> Compare and contrast `coord_cartesian()` vs `xlim()` or `ylim()` when zooming in on a histogram. What happens if you leave binwidth unset? What happens if you try and zoom so only half a bar shows?
>

```{r}
diamonds %>% ggplot() + 
	geom_histogram(mapping = aes(x = price)) +
	coord_cartesian(xlim = c(1000,3000), ylim = c(0, 1000))

diamonds %>% ggplot() +
	geom_histogram(aes(x=price)) +
	xlim(1000,3000)+
	ylim(0,1000)

```

# 7.4.1
## 1

>
> What happens to missing values in a histogram? What happens to missing values in a bar chart? Why is there a difference?
>

```{r}
diamonds %>% mutate(y = ifelse(y > 20, NA_real_, y)) %>%
	ggplot(aes(x = y)) +
	geom_histogram()

diamonds %>% mutate(cut = ifelse(cut=="Ideal", NA_character_, cut)) %>%
	ggplot(aes(x = cut)) +
	geom_bar()

```

## 2
>
> What does na.rm = TRUE do in mean() and sum()?
>

```{r}
mean(c(0, 1, 2, NA), na.rm = TRUE)
sum(c(0, 1, 2, NA), na.rm = TRUE)
```


# 7.5.1

## 1
>
> Use what you’ve learned to improve the visualization of the departure times of cancelled vs. non-cancelled flights.
>

```{r}
nycflights13::flights %>% 
	mutate(cancelled=is.na(dep_time), sche_dep=(sched_dep_time %/% 100)/(sched_dep_time %% 100)) %>%
	select(cancelled, sche_dep) %>% 
	ggplot()+
	geom_boxplot(aes(y=sche_dep, x=cancelled))
	
```

## 2
>
> What variable in the diamonds dataset is most important for predicting the price of a diamond? How is that variable correlated with cut? Why does the combination of those two relationships lead to lower quality diamonds being more expensive?
>

```{r}
broom::tidy(glm(diamonds$price ~ diamonds$carat + diamonds$cut + diamonds$color + diamonds$clarity))
```

## 3
>
> Install the ggstance package, and create a horizontal box plot. How does this compare to using `coord_flip()`?
>

```{r}
mpg %>% ggplot() +
	geom_boxplot(aes(x = class, y = hwy)) +
	coord_flip()
```

## 4
>
> One problem with box plots is that they were developed in an era of much smaller datasets and tend to display a prohibitively large number of “outlying values”. One approach to remedy this problem is the letter value plot. Install the lvplot package, and try using `geom_lv()` to display the distribution of price vs cut. What do you learn?
> How do you interpret the plots?
>

```{r}
library(lvplot)

diamonds %>% ggplot(aes(x=cut, y=price)) +
	geom_lv()
```

## 5
>
> Compare and contrast `geom_violin()` with a faceted `geom_histogram()`, or a colored `geom_freqpoly()`. What are the pros and cons of each method?
>

```{r}
diamonds %>% ggplot() +
	geom_violin(aes(x=cut, y=price))
```

`geom_violin` has a merit that distribution is easy to understand.

## 6
>
> If you have a small dataset, it’s sometimes useful to use `geom_jitter()` to see the relationship between a continuous and categorical variable. The ggbeeswarm package provides a number of methods similar to `geom_jitter()`. List them and briefly describe what each one does.
>

# 7.5.2
## 1
>
> How could you rescale the count dataset above to more clearly show the distribution of cut within color, or color within cut?
> 

`cut` within `color`
```{r}
library(viridis)

diamonds %>% count(color, cut) %>%
	group_by(color) %>%
	mutate(prop=n/sum(n)) %>%
	ggplot()+
	geom_tile(aes(x=color, y=cut, fill=prop))+
	scale_fill_viridis(limits=c(0,1))
```

`color` within `cut`
```{r}
diamonds %>% count(color, cut) %>%
	group_by(cut) %>%
	mutate(prop=n/sum(n)) %>%
	ggplot()+
	geom_tile(aes(x=color, y=cut, fill=prop))+
	scale_fill_viridis(limits=c(0,1))

```

## 2
>
> Use `geom_tile()` together with dplyr to explore how average flight delays vary by destination and month of year. What makes the plot difficult to read? How could you improve it?
>

```{r}
nycflights13::flights %>% 
	group_by(month, dest) %>%
	summarize(dep_delay = mean(dep_delay, na.rm = TRUE)) %>%
	ggplot(aes(x=factor(month), y=reorder(dest, dep_delay), fill=dep_delay)) +
	geom_tile() +
	scale_fill_viridis()
```
# 7.5.3
## 1
>
> Why is it slightly better to use aes(x = color, y = cut) rather than aes(x = cut, y = color) in the example above?
>

`cut_number`
```{r}
diamonds %>% ggplot(aes(color=cut_number(carat, 5), x=price)) +
	geom_freqpoly()
```

`cut_width`
```{r}
diamonds %>% ggplot(aes(color=cut_width(carat, 5), x=price)) +
	geom_freqpoly()

```

## 2

>
> Visualize the distribution of carat, partitioned by `price`.
>

```{r}
diamonds %>% ggplot(aes(x=cut_number(price, 10), y=carat)) +
	geom_violin() +
	coord_flip()
```

## 3
>
> How does the price distribution of very large diamonds compare to small diamonds. Is it as you expect, or does it surprise you?
>

## 4
> 
> Combine two of the techniques you’ve learned to visualize the combined distribution of cut, carat, and price.
> 

```{r}
diamonds %>% ggplot(aes(x=carat, y=price)) +
	geom_violin() + 
	facet_grid(~cut)
```

## 5
>
> Two dimensional plots reveal outliers that are not visible in one dimensional plots. For example, some points in the plot below have an unusual combination of x and y values, which makes the points outliers even though their x and y values appear normal when examined separately.
>
```{r}
ggplot(data = diamonds) +
  geom_point(mapping = aes(x = x, y = y)) +
  coord_cartesian(xlim = c(4, 11), ylim = c(4, 11))
```
> 
> Why is a scatterplot a better display than a binned plot for this case?
> 

If there is a strong relationships between `x` and `y`, then you should use scatterplot.
