---
title: "r4ds Ex 3.3.1"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
author: MW
output: pdf_document
---

```{r setup, include = FALSE}
library(ggplot2)
library(dplyr)
```


# 3.2.4
## 1
```{r, echo=FALSE}
ggplot(data=mpg) + 
  geom_point(mapping=aes(x=displ, y=hwy, color="blue"))
```
If `color="blue"` is in `aes`, then data are regarded to have categorical "blue". 

## 2
```{r}
mpg %>% select_if(is.character) %>% names
mpg %>% select_if(is.numeric) %>% names
```
categorical is `r mpg %>% select_if(is.character) %>% names()`
continuous is `r mpg %>% select_if(is.numeric) %>% names()`


## 3
e.g., I selected `displ`, `hwy`, and `cty` as well sample code.

##### color
```{r}
ggplot(mpg, aes(x=displ, y=hwy, color=cty)) +
  geom_point()
```

##### size
```{r}
ggplot(mpg, aes(x=displ, y=hwy, size=cty)) +
  geom_point()
```

##### shape
```{r, eval=FALSE}
ggplot(mpg, aes(x=displ, y=hwy, shape=cty)) +
  geom_point()
## error: A continuous variable can not be mapped to shape
```

## 4
```{r}
ggplot(mpg, aes(x=displ, y=hwy, color=cty, size=cty)) +
  geom_point()
```
You can run multiple `aes` but it is ineffective.

## 5
```{r, eval=FALSE}
vignette("ggplot2-specs")
```
Vignette file explain followings;
 `...the size of the stroke is controlled by stroke.`.

## 6

```{r}
ggplot(mpg, aes(x=displ, y=hwy, color=displ<5)) +
  geom_point()
```
You can run above code, like `color=displ<5`. The variables are divided to `TRUE` or `FALSE`.
