---
title: "r4ds Ex 3.6.1"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
author: MW
output: pdf_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
```


# 3.6.1
## 1
Line chart: `geom_line()`
Boxplot: `geom_boxplot()`
Histgram: `geom_histgram()`
Area chart: `geom_area`


## 2
x-axis: `displ`
y-axis: `hwy`
colored by `drv`
smooth line;
	standard error: none
	fitting by `drv`
```{r}
ggplot(data=mpg, mapping=aes(x=displ, y=hwy, color=drv)) + 
	geom_point() + 
	geom_smooth(se=FALSE)
```


## 3
`show.legend=FALSE` means to hide the legend box.


## 4
`se` argument determine confidence interval around smooth. By default, it shows 95% confidence interval.

## 5
```{r}
#install.packages("gridExtra")
library(gridExtra)
a <- ggplot(data=mpg, mapping=aes(x=displ, y=hwy)) + 
  geom_point() + 
  geom_smooth()

b <- ggplot() + 
  geom_point(data=mpg, mapping=aes(x=displ, y=hwy)) + 
  geom_smooth(data=mpg, mapping=aes(x=displ, y=hwy))

grid.arrange(a, b, nrow = 1)
```
These two plots are same, because `geom_` uses the first variables(`ggplot()`) unless each `geom_` specified dependency.

## 6
```{r}
library(gridExtra)

a <-  ggplot(data=mpg, aes(x=displ, y=hwy)) + 
  geom_point() + 
  geom_smooth(se=FALSE)

b <-  ggplot(data=mpg) + 
  geom_point(aes(x=displ, y=hwy)) + 
  geom_smooth(aes(x=displ, y=hwy, group=drv), se=FALSE)

c <- ggplot(data=mpg) + 
  geom_point(aes(x=displ, y=hwy, color=drv)) + 
  geom_smooth(aes(x=displ, y=hwy, color=drv), se=FALSE)

d <- ggplot(data=mpg) + 
  geom_point(aes(x=displ, y=hwy, color=drv)) + 
  geom_smooth(aes(x=displ, y=hwy), se=FALSE)

e <- ggplot(data=mpg) + 
  geom_point(aes(x=displ, y=hwy, color=drv)) + 
  geom_smooth(aes(x=displ, y=hwy, linetype=drv), se=FALSE)

f <- ggplot(data=mpg) + 
  geom_point(aes(x=displ, y=hwy, color=drv, fill=drv), color="white", pch=21)


```
