---
title: "r4ds Ex 3.5.1"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
author: MW
output: pdf_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
```


# 3.5.1
## 1
```{r, echo=FALSE}
ggplot(data=mpg) +
	geom_point(mapping=aes(x=displ, y=hwy)) +
	facet_grid(displ ~ cyl)
```
It is drawn for each continuous variable.

## 2
```{r}
ggplot(data=mpg) +
	geom_point(mapping=aes(x=hwy, y=cty)) +
	facet_grid(drv ~ cyl)
```
The empty cells shows no combinations of `drv` and `cyl` in itself.


## 3
`.` means ignoring dimensions. So, `drv ~ .` facet only `drv`.

## 4
```{r}
ggplot(data=mpg) +
	geom_point(mapping=aes(x=displ, y=hwy, color=class))
```
Colorized by `class`. 
### Facet
#### advantage
- Friendly to color blinders.
- Easy to see the relationsihp within `class`

#### disadvantage
- Increase the number of graphs by the number of catagories.

### Color
#### advantage
- Easy to see the relationship between `class`

#### disadvantage
- Difficult to see if the number of o¥bservation increases

## 5
`...nrow, ncol: Number of rows and columns.`
Because `facet_grid` automatically determined rows and cols.

## 6
If you don't use unique values, it's complicated.
