---
title: "r4ds Ex 3.7.1"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
author: MW
output: pdf_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
```


# 3.7.1
## 1
```{r}
ggplot(data=diamonds) +
	geom_pointrange(aes(x=cut, y=depth), stat="summary")
```

## 2
```{r}
library(gridExtra)
a <- ggplot(data=diamonds) +
	geom_col(aes(x=cut, y=depth))

b <- ggplot(data=diamonds) +
	geom_bar(aes(x=cut))

grid.arrange(a, b, nrow = 1)
```
`geom_col` uses `stat_identity`, so it requires `x` and `y` in aesthetics.
`geom_bar` uses `stat_count` by default, so it has possibility to change the `y` by specifying `stat`.

Example is as follows:
```{r}
ggplot(data=diamonds) +
	geom_bar(aes(x=cut, y=depth), stat="identity")
```

## 3
Correspondence list of `geom_` and `stat_`.
- `geom_bar` `stat_count`
- `geom_contour` `stat_contour`
- `geom_count` `stat_sum`
- `geom_density` `stat_density`
- `geom_histgram` `stat_bin`
- `geom_qq_line` `stat_qq_line`
- `geom_qq` `stat_qq`
- `geom_smooth` `stat_smooth`
- `geom_violin` `stat_violin`
- `geom_bin2d` `stat_bin_2d`
- `geom_boxplot` `stat_boxplot`
- `geom_density_2d` `stat_density_2d`
- `geom_hex` `stat_hex`
- `geom_freqpoly` `stat_bin`
- `geom_quantile` `stat_quantile`
- `geom_sf` `stat_sf`


## 4
```{r eval=FALSE}
stat_smooth
```
- `y`: predicted value
- `ymin`: lower value of the confidence interval
- `ymax`: upper value of the confidence interval
- `se`: standard error

The list of parameters that control the behavior is as follows:
- `method`
- `formula`
- `se`
- `na.rm`
- `show.legend`
- `inherit.aes`
- `n`
- `span`
- `fullrange`
- `level`
- `method.args`


## 5
```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, y = ..prop..))
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = color, y = ..prop..))
```
The problem is that the ratio calculation is done within the group.
Solutions;
```{r}
ggplot(data=diamonds) + 
	geom_bar(aes(x=cut, y=..prop.., group=1))

diamonds %>% 
	group_by(cut) %>% nest() %>% 
	inner_join(count(diamonds %>% group_by(cut))) %>% 
	mutate(s=.$n %>% sum) %>% unnest() %>% 
	ggplot(aes(x=cut, y=n/s, fill=color)) +
		geom_bar(stat="identity")

```

