---
title: "r4ds Ex 3.8.1"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
author: MW
output: pdf_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
```


# 3.8.1
## 1
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point(position="jitter")
```
Points in above plot are overlapped.

## 2
- `width`: determine the amount of vertical jitter.
- `height`: determine the amount of horizontal jitter. 
Both have 40% of the resolution of the data by default.

## 3
```{r}
a <- ggplot(mpg, aes(x=cty, y=hwy)) +
	geom_count()
b <- ggplot(mpg, aes(x=cty, y=hwy)) +
	geom_jitter()
c <- ggplot(mpg, aes(x=cty, y=hwy, color=class)) +
	geom_count()
d <- ggplot(mpg, aes(x=cty, y=hwy, color=class)) +
	geom_jitter()

gridExtra::grid.arrange(a, b, c, d, nrow=2)
```

- Left columns: `geom_count`  
- Right columns: `geom_jitter`  
- Upper rows: Non-classificated by `class`  
- Lower rows: Classificated by `class`  


If you have lots of observations, you should use `geom_count` rather than `geom_jitter`.
But you would use `geom_jitter` if you use combination `geom_` and `color`.


## 4
The default is `position="dodge2"` which control not horizontal but only vertical.
```{r}
ggplot(data=mpg, aes(x=drv, y=hwy, color=class)) +
	geom_boxplot()
```
So you set `position="identity"` when you want to align vertically.
```{r}
ggplot(data=mpg, aes(x=drv, y=hwy, color=class)) +
	geom_boxplot(position="identity")
```

