---
title: "r4ds Ex 5.2.4"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
author: MW
output: pdf_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
```


# 5.2.4
## 1
> Find all flights that
> > 1. Had an arrival delay of two or more hours
> > 2. Flew to Houston (IAH or HOU)
> > 3. Were operated by United, American, or Delta
> > 4. Departed in summer (July, August, and September)
> > 5. Arrived more than two hours late, but didn’t leave late
> > 6. Were delayed by at least an hour, but made up over 30 minutes in flight
> > 7. Departed between midnight and 6 am (inclusive)

### 1 
```{r}
flights %>% filter(arr_delay>=120)
```

### 2
```{r}
flights %>% filter(dest=="IAH" | dest=="HOU")
```

### 3
```{r}
flights %>% filter(carrier %in% c("AA", "DL", "UA"))
```

### 4
```{r}
flights %>% filter(month>=7, month<=9)
```

### 5
```{r}
flights %>% filter(arr_delay>120, dep_delay<=0)
```

### 6 
```{r}
flights %>% filter(dep_delay>=60, dep_delay-arr_delay>30)
```

### 7
```{r}
flights %>% filter(dep_time==2400 | dep_time<=600)
```


## 2
> Another useful dplyr filtering helper is `between()`. What does it do? Can you use it to simplify the code needed to answer the previous challenges?  

`between(x, left, right)` is a shortcut for `x >= left & x <= right`.


## 3
> How many flights have a missing `dep_time`? What other variables are missing? What might these rows represent?  

```{r}
flights %>% filter(dep_time %>% is.na())
```

## 4
> Why is `NA ^` 0 not missing? Why is` NA | TRUE` not missing? Why is `FALSE & NA` not missing? Can you figure out the general rule? (`NA * 0` is a tricky counterexample!)  

`x` in followings is any values.
- `NA^0==1` because `x^0==1`
- `NA | TRUE` is `TRUE` because `x | TRUE` always return `TRUE`.
- `FALSE & NA` is `FALSE` because `x & FALSE` always return `FALSE`.

