---
title: "r4ds Ex 5.4.1"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
author: MW
output: pdf_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
```


# 5.4.1
## 1
> Brainstorm as many ways as possible to select `dep_time`, `dep_delay`, `arr_time`, and `arr_delay `from flights.

The simplest way is as follows;
```{r}
flights %>% select(dep_time, dep_delay, arr_time, arr_delay)
```

Others are as follows;
```{r}
tmp <- c("dep_time", "dep_delay", "arr_time", "arr_delay")
flights %>% select(tmp)
```
```{r}
flights %>% select(contains("_time"), contains("_delay"))
```

## 2
  
> What happens if you include the name of a variable multiple times in a `select() call? 

It is selected only once no matter how many times you call.

## 3
  
> What does the `one_of()` function do? Why might it be helpful in conjunction with this vector?  

This is useful when you have the column names you want to select as a string vector.

## 4
  
> Does the result of running the following code surprise you? How do the select helpers deal with case by default? How can you change that default?

```{r}
select(flights, contains("TIME"))
```

By default, `contains()` ignores case. If you don't want to, you should use `ignore.case=FALSE`.

