---
title: "r4ds Ex 5.5.2"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
author: MW
output: pdf_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
```


# 5.5.2
## 1
  
> Currently `dep_time` and `sched_dep_time` are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.

```{r}
tomin <- function(nm){
	ifelse(is.na(nm), NA,
	ifelse(nchar(nm)<=2, nm, 
		 (nm %>% str_sub(start=1, end=-3) %>% as.numeric())*60 + 
			nm %>% str_sub(start=-2, end=-1) %>% as.numeric()
	)
	)
}

flights %>% select(dep_time, sched_dep_time) %>% 
	mutate(dep_min=tomin(dep_time), sched_dep_min=tomin(sched_dep_time))
```

## 2
  
> Compare `air_time` with `arr_time - dep_time`. What do you expect to see? What do you see? What do you need to do to fix it?

```{r}
smpl2 <- flights %>% 
	mutate(arr_dep=(arr_time %>% tomin)-(dep_time %>% tomin), dif=air_time-arr_dep) %>% 
	select(air_time, arr_dep, dif)
smpl2 %>% ggplot(aes(x=air_time, y=dif)) +
	geom_point()
```

If `air_time` and `arr_dep` is equal, `y = x` line is expected.
Negative y-axis values show to span Time Zone.


## 3
  
> Compare `dep_time`, `sched_dep_time`, and `dep_delay`. How would you expect those three numbers to be related?

```{r}
smpl3 <- flights %>% 
	mutate(dif=tomin(dep_time)-tomin(sched_dep_time)) %>% 
	select(dif, dep_delay)
smpl3 %>% ggplot(aes(x=dep_delay, y=dif)) +
	geom_point()
```

If `dep_min` and `sched_dep_min` is equal, `y = x` line is expected.
Negative y-axis values show to span Time Zone.


## 4
  
> Find the 10 most delayed flights using a ranking function. How do you want to handle ties? Carefully read the documentation for `min_rank()`.

```{r}
flights %>%
	select(contains("delay")) %>% 
	mutate(dep_min=min_rank(desc(dep_delay)), arr_min=min_rank(desc(arr_delay))) %>% 
	filter(dep_min<=10 | arr_min<=10)
```

## 5

> What does `1:3 + 1:10` return? Why?


The process between Vector1 and Vector2 can run till Vector2's loop finish. But the size doesn't match, then Vector1 repeats.

## 6

> What trigonometric functions does R provide?

`?trigonometric`




