---
title: "r4ds Ex 5.7.1"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
author: MW
output: pdf_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
```


# 5.7.1
## 1
  
> Refer back to the lists of useful mutate and filtering functions. Describe how each operation changes when you combine it with grouping.

skip...


## 2
  
> Which plane (`tailnum`) has the worst on-time record?


```{r}
flights %>% group_by(tailnum) %>%
	summarize(arr_delay = mean(arr_delay)) %>%
	filter(min_rank(desc(arr_delay)) == 1)
```

`N844MH` is worst on time record.

## 3
  
> What time of day should you fly if you want to avoid delays as much as possible?

```{r}
flights %>% group_by(hour, minute) %>%
	summarize(arr_delay = mean(arr_delay, na.rm = TRUE)) %>%
	arrange(arr_delay)
```

If you want not to get on delayed airplane, you should use an airplane from an early morning.

## 4
  
> For each destination, compute the total minutes of delay. For each flight, compute the proportion of the total delay for its destination.

```{r}
flights %>% group_by(dest) %>% 
	mutate(sum_delay=sum(arr_delay, na.rm=TRUE), prop_delay=arr_delay/sum_delay)
```

## 5

> Delays are typically temporally correlated: even once the problem that caused the initial delay has been resolved, later flights are delayed to allow earlier flights to leave. Using `lag()` explore how the delay of a flight is related to the delay of the immediately preceding flight.

```{r}
flights %>% group_by(origin) %>% 
	mutate(delaylag = lag(dep_delay)) %>% 
	filter(!is.na(dep_delay), !is.na(delaylag)) %>% 
	group_by(delaylag) %>% 
	summarize(delaymean=mean(dep_delay)) %>% 
	ggplot(aes(x=delaylag, y=delaymean))+
		geom_point()
```

## 6

> Look at each destination. Can you find flights that are suspiciously fast? (i.e. flights that represent a potential data entry error). Compute the air time of a flight relative to the shortest flight to that destination. Which flights were most delayed in the air?


## 7

> Find all destinations that are flown by at least two carriers. Use that information to rank the carriers.

## 8

> For each plane, count the number of flights before the first delay of greater than 1 hour.
