---
title: "r4ds Ex 10"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
author: MW
output: pdf_document
---

```{r setup, include = FALSE}
library(tidyverse)
```


# 10.5
## 1
>    
>	How can you tell if an object is a tibble? (Hint: try printing mtcars, which is a regular data frame).
> 

```{r}
mtcars
```
  
If data is NOT tibble, basically all the values are returned.

```{r}
mtcars %>% as_tibble()
```
  
On the other hands, data type in columns is unique, and top 10 rows of data are returned by default.

## 2
>  
> Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behaviours cause you frustration?
>

```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
```


```{r}
df <- tibble(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
```

## 3
>
> If you have the name of a variable stored in an object, e.g. var <- "mpg", how can you extract the reference variable from a tibble?
>

## 4
>  
> Practice referring to non-syntactic names in the following data frame by:
> > 1. Extracting the variable called 1.	
> > 2. Plotting a scatterplot of 1 vs 2.
> > 3. Creating a new column called 3 which is 2 divided by 1.
> > 4. Renaming the columns to one, two and three.
```{r}
annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)
```

```{r}
annoying[[1]]
annoying %>% ggplot(aes(x=`1`, y=`2`)) +
	geom_point()
annoying <- annoying %>% mutate(`3` = `2` / `1`)
annoying
annoying %>% rename(one = `1`, two = `2`, three = `3`)
```

## 5
> 
> What does tibble::enframe() do? When might you use it?
> 

```{r}
enframe(c(a=1, b=2, c=3))
```

## 6
>
> What option controls how many additional column names are printed at the footer of a tibble?
> 
  
```
?print.tbl
```

```
n_extra: Number of extra columns to print abbreviated information for,
          if the width is too small for the entire tibble. If ‘NULL’,
          the default, will print information about at most
          ‘tibble.max_extra_cols’ extra columns.
```
